Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-06-07 paper.qmd
address observation from reviewer 5 regarding Figure lables/titles and numbering of equations. (Luckily) the position of the last image is now not in the middle of the References.

crossref:
  eq-title: Equation     # (default is "")
  fig-prefix: Fig.   # (default is "Figure")
  # tbl-prefix: table    # (default is "Table")
  ref-hyperlink: false # (default is true)
  fig-title: Fig.

@@

$$
p_k = \varepsilon_k \int_a \rho(\vec{x}) \sigma_k(\vec{x}) da
$$

@@

$$
p_k = \varepsilon_k \sum_h \rho(h) \sigma_k(h).
$$

@@

Regarding the aircraft-debris encounter geometry, this yields to two conceptual considerations:
1. if the aircraft were stationary, the area exposed to the debris impact would be the top face of the rectangular solid, and
2. if the debris were stationary, it would be the front face.

@@

$$
\begin{aligned}
P &= \Delta A \times \sigma(\varphi, i) = 1000 \times \sigma\Bigl(\frac{\pi}{6}, \frac{\pi}{4}\Bigl) \\
  &= 1000 \times \num{2.490756e-15} = \num{2.490756e-12}
\end{aligned}
$$

@@

$$ \sigma(\varphi) = \frac{1}{N} \sum_{k = 1}^N \sigma(\varphi, i_k)$$

@@

$$
 E_{h, H} =  \sum_t W_H(h) \cdot \rho_{t,H}(h) \cdot \varepsilon_t
$$

>>>>

crossref:
  # eq-title: Equation     # (default is "")
  fig-prefix: Fig.   # (default is "Figure")
  fig-title: Fig.
  # tbl-prefix: table    # (default is "Table")
  ref-hyperlink: false # (default is true)

@@

$$
p_k = \varepsilon_k \int_a \rho(\vec{x}) \sigma_k(\vec{x}) da
$$ {#eq-impact-probability-general}

@@

$$
p_k = \varepsilon_k \sum_h \rho(h) \sigma_k(h).
$$ {#eq-impact-probability-h3}

@@

Regarding the aircraft-debris encounter geometry, this yields to two conceptual considerations:

1. if the aircraft were stationary, the area exposed to the debris impact would be the top face of the rectangular solid, and
2. if the debris were stationary, it would be the front face.

@@

$$
\begin{aligned}
P &= \Delta A \times \sigma(\varphi, i) = 1000 \times \sigma\Bigl(\frac{\pi}{6}, \frac{\pi}{4}\Bigl) \\
  &= 1000 \times \num{2.490756e-15} = \num{2.490756e-12}
\end{aligned}
$$ {#eq-impact-probability-example}

@@

$$
\sigma(\varphi) = \frac{1}{N} \sum_{k = 1}^N \sigma(\varphi, i_k)
$$ {#eq-debris-impact-probability-historical}

@@

$$
 E_{h, H} =  \sum_t W_H(h) \cdot \rho_{t,H}(h) \cdot \varepsilon_t
$$ {#eq-impact-probability-hourly}
